---
title: "Project 1"
author: "Kupriyanov Semyon"
date: "07 11 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Project 1

### Short description:
Presents data on the Olympic Games over the past 120 years.
The dataset has the following features:

*ID* – Unique number for each athlete
*Name* – Athlete's name
*Sex* – M or F
*Age* – Integer
*Height* – In centimeters
*Weight* – In kilograms
*Team* – Team name
*NOC* – National Olympic Committee 3-letter code
*Games* – Year and season
*Year* – Integer
*Season* – Summer or Winter
*City*– Host city
*Sport* – Sport
*Event* – Event
*Medal* – Gold, Silver, Bronze, or NA

In this work, a statistical analysis of some data was carried out and a number of indicators were identified.

### Task 1.
#### Loading and collecting data.
The data is split into several files, presented in the "Data_folder" directory.
To assemble data into a single dataset, the *"integrator"* function was written.
The function takes two arguments: the path to the files, the extension of the files to be merged. *Both arguments must be strings*.
```{r}
integrator <- function(path_to_file, ind){
  setwd(path_to_file) #change the directory to the one specified in the argument
  names_of_files <- dir(getwd()) #vector with all files in directory
  is_ind <- function(x, ind){
    parts <- strsplit(x,".",fixed=TRUE)
    nparts <- length(parts[[1]]) 
    return(parts[[1]][nparts] == ind) 
  } #function that determines the presence of the extension ind
  mk_table_csv <- function(x){
    return(read.csv(x))
  } #opens the file with read.csv 
  mk_table_table <- function(x){
    return(read.table(x)) 
  } #opens the file with read.table
  table_maker <- function(named_vector, mk_table_f){
    just_table <- mk_table_f(named_vector[1])
    for (i in named_vector[-1]){
      just_table <- rbind(just_table, mk_table_f(i))
    }
    return(just_table)
  } #concatenates files from the specified vector into one
  if (ind == "csv"){
    finish_table <- table_maker(names_of_files[sapply(names_of_files,is_ind, ind)], mk_table_csv)
    
  } else{
    finish_table <- table_maker(names_of_files[sapply(names_of_files,is_ind, ind)], mk_table_table)
    
  }
  return(finish_table)
}
```
An example of a function call:
*integrator("C:/Users/username/OneDrive/Desktop/Project", "csv")*
Upload the file:
```{r}
#path <- readline(prompt="Enter path to file: ")
#ind <- readline(prompt="Enter index, for example, 'csv': ")
path <- "C:/Users/pfft/OneDrive/Рабочий стол/БИ/R stat/Проект 1/Project"
ind <- "csv"
olimpic <- integrator(path, ind)
```
The data is loaded as an *olimpic* dataframe.


### Task 2.
Editing data.
The data structure was looked at:
```{r}
str(olimpic)
```
All nominative variables with a small number of grades were converted to factors. After the transformation, the data structure became more accessible for initial assessment.
```{r, echo=FALSE}
olimpic$Sex <- factor(olimpic$Sex) 
olimpic$NOC <- factor(olimpic$NOC) 
olimpic$Sport <- factor(olimpic$Sport) 
olimpic$Season <- factor(olimpic$Season) 
olimpic$Medal <- factor(olimpic$Medal) 
olimpic$Team <- factor(olimpic$Team)
```

```{r}
str(olimpic)
```

The trait *sex* revealed unnecessary gradations ('', G). The *Games* column duplicates information from the Season and Year columns. This is contrary to the concept of tidy date; the column can be removed.After deletion, the underlying statistics of quantitative factors can be viewed using the *summary()* function:

```{r}
olimpic$Games <- NULL
summary(olimpic)
```

The presence of additional empty factors in the variables *Sex*, *Age*, *Medal*, *Season* was revealed. Incorrect values are observed in the variables *Age*, *Height*, *Weight* (max in Age = 240 years, max in Height = 340 cm, min in Weight = 7 kg). The *dplyr* package was used to correct the data.

```{r, echo=FALSE}
library(dplyr)
```

```{r, echo=FALSE}
olimpic_cor <- olimpic %>% mutate(Age = sapply(olimpic$Age, function(x) ifelse(x>66, NA, x)))# corrected age
olimpic_cor <- olimpic_cor %>% mutate(Height = sapply(olimpic$Height, function(x) ifelse(x>230, NA, x)))# corrected growth
olimpic_cor <- olimpic_cor %>% mutate(Sex = sapply(olimpic$Sex, function(x) ifelse(x=="F", "F", ifelse(x=="M", "M", NA))))
olimpic_cor$Sex <- factor(olimpic_cor$Sex)# fixed the floor
olimpic_cor <- olimpic_cor %>% mutate(Season = sapply(olimpic$Season, function(x) ifelse(x=="Summer", "Summer", ifelse(x=="Winter", "Winter", NA))))
olimpic_cor$Season <- factor(olimpic_cor$Season)# corrected the season
olimpic_cor <- olimpic_cor %>% mutate(Medal = sapply(olimpic$Medal, function(x) ifelse(x=="Bronze", "Bronze", ifelse(x=="Gold", "Gold", ifelse(x=="Silver", "Silver", NA)))))
olimpic_cor$Medal <- factor(olimpic_cor$Medal)# fixed medals
```

```{r}
summary(olimpic_cor)
```

The corrected data is presented in the form of *olimpic_cor* dataframe.
Initial data preparation is completed. Another way of viewing data and correcting them is graphical. You can build graphs, like boxplots, scatterplots, etc., to estimate emissions or other indicators. This approach was applied to other tasks during the work on sorted and filtered data, since the initial data is quite massive and their rendering does not always give a clear picture. Also, NA values have not been replaced or removed at this stage. This has also been done in other parts of the work on filtered and sorted data(to avoid data loss).

### Task 3.
The age of the youngest athletes of both sexes at the 1992 Olympics was established.For this task, the functionality of the *dplyr* package was used. The data was first filtered and sorted, the NA values were removed only for the feature of interest.Missing values have been removed after filtering and sorting the data using the min option *na.rm = T*.
```{r}
olimpic_cor %>% group_by(Sex) %>% filter(Year == 1992) %>% select(Age, Sex) %>% summarise(Min_Age = min(Age, na.rm = T))

```
The minimum age *for females* was *12* years old, *for males* was *11* years old.

### Task 4.
The *mean* and *standard deviation* of the *Height* variable were calculated for athletes of each gender. Missing values have been removed after filtering and sorting the data using the *mean* and *sd* option *na.rm = T*.
```{r}
olimpic_cor %>% filter(Sex == "M" | Sex == "F") %>% group_by(Sex) %>% summarise(mean_height = mean(Height, na.rm = T), sd_height = sd(Height, na.rm = T))

```
For women, the mean and standard deviation of height was *168*, *8.78*, respectively. For men, the mean and standard deviation of height was *179*, *9.36*, respectively.

### Task 5.
The *mean* and *standard deviation* of the *Height* variable were calculated for *female tennis players (sex = F) at the 2000 Olympics*. Missing values have been removed after filtering and sorting the data using the *mean* and *sd* option *na.rm = T*. The answer was rounded to the first character after the separator.
```{r}
olimpic_cor %>% filter(Year == 2000 & Sex == "F" & Sport == "Tennis") %>% summarise(Tennis_female_mean_height = round(mean(Height, na.rm = T), digits = 1), Tennis_female_sd_height = round(sd(Height, na.rm = T), digits = 1))

```
The *average* was *171.8* cm; the standard deviation was *6.5* cm.

### Task 6.
The sport with the hardest participant in the 2006 Olympics was determined.
```{r}
hard_sport_2006 <- olimpic_cor %>% filter(Year == 2006) 
hard_sport_2006[which.max(hard_sport_2006$Height), c(2, 13)]
```
The heaviest competitor in the 2006 Olympics was *Zdeno Chra*; sport - *Ice Hockey*.

### Task 7.
The number of *gold medals* received by *women from 1980 to 2010* was determined.
```{r}
olimpic_cor %>% filter(Year >= 1980 & Year <= 2010 & Sex == "F" & Medal == "Gold") %>% summarise(Number_of_gold_medals = n())

```
*2,249 gold medals* were received.

### Task 8.
In this part of the work, the athlete *John Aalberg* was studied. The number of his participation in the Olympic Games was investigated.
First, the data was filtered with the following result:
```{r}
olimpic_cor %>% filter(Name == "John Aalberg") %>% select(Year, Name)
```

They determined that *John Aalberg* participated *8* times, 4 times in 1992 and 4 times in 1994. The viewing range was expanded:

```{r}
olimpic_cor %>% filter(Name == "John Aalberg") %>% select(Year, Season, Name, Event)

```
Thus, *John Aalberg* participated in the Olympic Games *twice*: in *1992* and *1994*. He took part in *4 competitions* at once.

### Task 9.
The analysis of the age groups of the participants in the 2008 Olympic Games was carried out. The athletes were divided into the following age groups: *[15-25)*, *[25-35)*, *[35-45)*, *[45-55]*. The following results were obtained:
```{r}
olimpic_2008_periods <- olimpic_cor %>% mutate(Age_period = sapply(olimpic_cor$Age, function(x) ifelse(x<25 & x>=15, "15-24", ifelse(x<35 & x>=25, "25-34", ifelse(x<45 & x>=35, "35-44", ifelse(x<=55 & x >=45, "45-55", "Other"))))))
olimpic_2008_periods$Age_period <- factor(olimpic_2008_periods$Age_period)
olimpic_2008_periods %>% group_by(Age_period) %>% summarise(Count = n())
```
The results were visualized on a graph using the *ggplot 2* library (in addition, the gender distribution was visualized):
```{r, echo=FALSE}
library(ggplot2)
ggplot(olimpic_2008_periods,aes(x = Age_period, fill = Sex))+
  geom_histogram(stat = "count")+
  labs(y = "Quantity", x = "Age periods",fill= "Participant gender" , title = "Age group chart at the 2008 Olympics")+
  theme_bw()
```
Thus, the two most represented age groups are: *[15-25)*, *[25-35)*. This is due to the fact that the main professional activity and career of athletes falls on this age period (~20-30 years). The sex composition shows that male athletes prevail in all age groups.

### Task 10.
The dynamics of *the number of sports* in the *2002* Olympics compared to the *1994* Olympics was analyzed.
```{r, echo=FALSE}
Sports <- olimpic_cor %>% filter(Year == 1994 | Year == 2002) %>% group_by(Year, Sport) %>% summarise(n()) 
Sports$Year <- factor(Sports$Year)
ggplot(Sports, aes(x = Year, fill = Sport))+
  geom_histogram(stat = "count")+
  scale_y_continuous(name = "Number of sports", breaks = c(1:15))+
  theme_bw()
```
*Three new sports* are present in 2002 compared to 1994 (*15* versus *12* sports, respectively). These sports are: *Curling*, *Skeleton*, *Snowboarding*.

### Task 11.
For each season, the *top 3 countries* were identified *for each type of medal*.

```{r}
# Gold
olimpic_cor %>% group_by(Season, NOC) %>% filter(Medal == "Gold", Season == "Winter") %>% summarise(num_for_gold = n()) %>% arrange(desc(num_for_gold)) %>% slice(1:3)
olimpic_cor %>% group_by(Season, NOC) %>% filter(Medal == "Gold", Season == "Summer") %>% summarise(num_for_gold = n()) %>% arrange(desc(num_for_gold)) %>% slice(1:3)
# Silver
olimpic_cor %>% group_by(Season, NOC) %>% filter(Medal == "Silver", Season == "Winter") %>% summarise(num_for_silver = n()) %>% arrange(desc(num_for_silver)) %>% slice(1:3)
olimpic_cor %>% group_by(Season, NOC) %>% filter(Medal == "Silver", Season == "Summer") %>% summarise(num_for_silver = n()) %>% arrange(desc(num_for_silver)) %>% slice(1:3)
# Bronze
olimpic_cor %>% group_by(Season, NOC) %>% filter(Medal == "Bronze", Season == "Winter") %>% summarise(num_for_bronze = n()) %>% arrange(desc(num_for_bronze)) %>% slice(1:3)
olimpic_cor %>% group_by(Season, NOC) %>% filter(Medal == "Bronze", Season == "Summer") %>% summarise(num_for_bronze = n()) %>% arrange(desc(num_for_bronze)) %>% slice(1:3)

```

### Task 12.
*Z-standardization* was carried out for the variable *Height*.Missing values have been removed after filtering and sorting the data using the *mean* and *sd* option *na.rm = T* (ensuring the correct operation of functions).The implementation was done using the basic R functionality.
```{r}
Height_z_scores <- (olimpic_cor$Height - mean(olimpic_cor$Height, na.rm = T))/sd(olimpic_cor$Height, na.rm = T)
olimpic_cor$Height_z_scores <- Height_z_scores
str(olimpic_cor)
```

### Task 13.
*Min-max normalization* was applied to the *Height* variable.The implementation was done using the *dplyr* functionality.
```{r, echo=FALSE}
olimpic_cor <- olimpic_cor %>% mutate(Height_min_max_scaled = (olimpic_cor$Height - min(olimpic_cor$Height, na.rm = T))/(max(olimpic_cor$Height, na.rm = T)-min(olimpic_cor$Height, na.rm = T)))
```

```{r}
str(olimpic_cor)
```


### Task 14.
Statistical analysis of the Age, Height, Weight variables was performed.
At the first step, the mean and standard deviation were calculated in the respective groups:
```{r, echo=FALSE}
olimpic_cor %>% filter(Season == "Winter") %>% group_by(Sex) %>% summarise(Mean_Age = mean(Age, na.rm = T), Sd_Age = sd(Age, na.rm = T))
olimpic_cor %>% filter(Season == "Winter") %>% group_by(Sex) %>% summarise(Mean_Height = mean(Height, na.rm = T), Sd_Height = sd(Height, na.rm = T))
olimpic_cor %>% filter(Season == "Winter") %>% group_by(Sex) %>% summarise(Mean_Weight = mean(Weight, na.rm = T), Sd_Weight = sd(Weight, na.rm = T))

```

To study the differences in these quantitative traits in the two sex groups, a comparison of the sample means was chosen. To determine the statistical test, a graphical analysis of the distributions of these quantities was carried out.

#### Age distribution:
```{r, echo=FALSE}
#transform data
winter_games <- olimpic_cor %>% filter(Season == "Winter") %>% group_by(Sex) %>% select(Sex, Age, Height, Weight)
# Visualizing the distributions separately for the Sex value
ggplot(winter_games, aes(x = Age, fill = Sex))+
  geom_histogram(stat = "count")+
  facet_grid(. ~ Sex)+
  theme_bw()
```

#### Height distribution:
```{r, echo=FALSE}
ggplot(winter_games, aes(x = Height, fill = Sex))+
  geom_histogram(stat = "count")+
  facet_grid(. ~ Sex)
  theme_bw()
```

#### Weight distribution:
```{r, echo=FALSE}
ggplot(winter_games, aes(x = Weight, fill = Sex))+
  geom_histogram(stat = "count")+
  facet_grid(. ~ Sex)+
  theme_bw()
```

*QQ-plots* were also built:

#### Age distribution for women:
```{r, echo=FALSE}
qqnorm(winter_games$Age[winter_games$Sex == "F"])
qqline(winter_games$Age[winter_games$Sex == "F"])
```
#### Age distribution for men:
```{r, echo=FALSE}
qqnorm(winter_games$Age[winter_games$Sex == "M"])
qqline(winter_games$Age[winter_games$Sex == "M"])
```
#### Height distribution for women:
```{r, echo=FALSE}
qqnorm(winter_games$Height[winter_games$Sex == "F"])
qqline(winter_games$Height[winter_games$Sex == "F"])
```
#### Height distribution for men:
```{r, echo=FALSE}
qqnorm(winter_games$Height[winter_games$Sex == "M"])
qqline(winter_games$Height[winter_games$Sex == "M"])
```
#### Weight distribution for women:
```{r, echo=FALSE}
qqnorm(winter_games$Weight[winter_games$Sex == "F"])
qqline(winter_games$Weight[winter_games$Sex == "F"])
```
#### Weight distribution for men:
```{r, echo=FALSE}

qqnorm(winter_games$Weight[winter_games$Sex == "M"])
qqline(winter_games$Weight[winter_games$Sex == "M"])
```

Based on the visualization results, it was concluded that the *distribution for the Age and Weight variables is not normal distribution* (especially for the Age variable). The *Height* variable has a fairly *close to normal distribution*. Thus, to analyze the difference in the means, the *t-test (Student's test)* was applied to the Height variable; for the Age and Weight variables, the *nonparametric* test, *Mann-Whitney test* was used.

The nonparametric Mann-Whitney test was chosen in part because the Age and Weight distributions showed *one-sided bias* in both sex groups.

For both the t-test and the Mann-Whitney test, a *two-sample option* was used (to compare the means of the two samples). Since the initial study of the data found that the means of all three variables in the male groups were higher, the *one-sided versions* of the t-test and the Mann-Whitney test were used.

#### Age testing:
```{r}
Age_test <- wilcox.test(winter_games$Age[winter_games$Sex == "M"], winter_games$Age[winter_games$Sex == "F"], alternative="greater")
cat("Method: ", Age_test$method,"Statistic: ", Age_test$statistic, "p-value: ", Age_test$p.value)

```
#### Weight testing:
```{r}
Weight_test <-wilcox.test(winter_games$Weight[winter_games$Sex == "M"], winter_games$Weight[winter_games$Sex == "F"], alternative="greater")
wilcox.test(winter_games$Weight[winter_games$Sex == "M"], winter_games$Weight[winter_games$Sex == "F"], alternative="greater")
cat("Method: ", Weight_test$method,"Statistic: ", Weight_test$statistic, "p-value: ", Weight_test$p.value)

```
#### Height testing:
```{r}
Height_test <- t.test(winter_games$Height[winter_games$Sex == "M"], winter_games$Height[winter_games$Sex == "F"], alternative="greater")
t.test(winter_games$Height[winter_games$Sex == "M"], winter_games$Height[winter_games$Sex == "F"], alternative="greater")
cat("Method: ", Height_test$method,"Statistic: ", Height_test$statistic, "p-value: ", Height_test$p.value, "Df:", Height_test$parameter)
```


#### The results are presented in the graphs:
```{r, echo=FALSE}
ggplot(winter_games, aes(x = Sex, y = Age))+
  geom_boxplot()+
  labs(y = "Sex", x = "Age", title = "Comparison of age by sex group")+
  theme_bw()
```

```{r, echo=FALSE}
ggplot(winter_games, aes(x = Sex, y = Height))+
  geom_boxplot()+
  labs(y = "Sex", x = "Height", title = "Comparison of height by sex group")+
  theme_bw()
```

```{r, echo=FALSE}
ggplot(winter_games, aes(x = Sex, y = Weight))+
  geom_boxplot()+
  labs(y = "Sex", x = "Weight", title = "Comparison of weight by sex group")+
  theme_bw()
```
A large number of emissions were recorded. Compare the height, weight and ages of men and women who competed in the Winter Olympics. Please format the results so that we can immediately use them for the article. (5 points)

Statistical analysis of the Age, Height, Weight variables was performed.

At the first step, the mean and standard deviation were calculated in the respective groups:

To study the differences in these quantitative traits in the two sex groups, a comparison of the sample means was chosen. To determine the statistical test, a graphical analysis of the distributions of these quantities was carried out.

transform data

Visualizing the distributions separately for the Sex value

Weight distribution

QQ-plots were also built:

Weight distribution for men

Based on the visualization results, it was concluded that the distribution for the Age and Weight variables is not normal (especially for the Age variable). The Height variable has a fairly close to normal distribution. Thus, to analyze the difference in the means, the t-test (Student's test) was applied to the Height variable; for the Age and Weight variables, the nonparametric Mann-Whitney test was used.

The nonparametric Mann-Whitney test was chosen in part because the Age and Weight distributions showed one-sided bias in both sex groups.

For both the t-test and the Mann-Whitney test, a two-sample option was used (to compare the means of the two samples). Since the initial study of the data found that the means of all three variables in the male groups were higher, the one-sided versions of the t-test and the Mann-Whitney test were used.

Age testing:

The results are presented in the graphs:

The data were analyzed for outliers.
A large number of outliers were recorded. With a large number of observations, the t-test is sufficiently robust to outliers, and nonparametric tests are initially robust to outliers. However, a parallel check was carried out. Outliers have been removed by filtration. The parameters for filtering were set using boxplots.

```{r}
winter_games2 <- winter_games %>% filter(Age < 37 & Age > 12)
winter_games2 <- winter_games2 %>% filter(Sex == "F" & Height < 182 & Height > 149 | Sex == "M" & Height < 196 & Height > 160)
winter_games2 <- winter_games2 %>% filter(Sex == "F" & Weight < 75 & Height > 49 | Sex == "M" & Weight < 101)

```

The tests were re-run.
#### Age testing 2:
```{r}
Age_test2 <- wilcox.test(winter_games2$Age[winter_games2$Sex == "M"], winter_games2$Age[winter_games2$Sex == "F"], alternative="greater")
cat("Method: ", Age_test2$method,"Statistic: ", Age_test2$statistic, "p-value: ", Age_test2$p.value)

```
#### Weight testing 2:
```{r}
Weight_test2 <-wilcox.test(winter_games2$Weight[winter_games2$Sex == "M"], winter_games2$Weight[winter_games2$Sex == "F"], alternative="greater")
wilcox.test(winter_games2$Weight[winter_games$Sex == "M"], winter_games2$Weight[winter_games2$Sex == "F"], alternative="greater")
cat("Method: ", Weight_test2$method,"Statistic: ", Weight_test2$statistic, "p-value: ", Weight_test2$p.value)

```
#### Height testing 2:
```{r}
Height_test2 <- t.test(winter_games2$Height[winter_games2$Sex == "M"], winter_games2$Height[winter_games2$Sex == "F"], alternative="greater")
t.test(winter_games2$Height[winter_games2$Sex == "M"], winter_games2$Height[winter_games2$Sex == "F"], alternative="greater")
cat("Method: ", Height_test2$method,"Statistic: ", Height_test2$statistic, "p-value: ", Height_test2$p.value, "Df:", Height_test2$parameter)
```

#### The filtered data plots are shown below:

```{r, echo=FALSE}
ggplot(winter_games2, aes(x = Sex, y = Age))+
  geom_boxplot()+
  labs(y = "Sex", x = "Age", title = "Comparison of age by sex group")+
  theme_bw()
```

```{r, echo=FALSE}
ggplot(winter_games2, aes(x = Sex, y = Height))+
  geom_boxplot()+
  labs(y = "Sex", x = "Height", title = "Comparison of height by sex group")+
  theme_bw()
```

```{r, echo=FALSE}
ggplot(winter_games2, aes(x = Sex, y = Weight))+
  geom_boxplot()+
  labs(y = "Sex", x = "Weight", title = "Comparison of weight by sex group")+
  theme_bw()
```

Thus, outliers did not significantly affect the values of the statistics probably due to the large number of observations.

On the basis of statistical checks, we can say that in men, age, height and weight differ significantly in a larger direction from women. Nevertheless, on the basis of boxplots, it can be seen that differences in age are not significantly expressed. The statistical significance is probably related to the large number of observations.

#### Thus, it is safe to say that the height and weight of male athletes at the Winter Olympic Games is significantly greater than that of female athletes.

### Task 15.
The variables *Team* and *Medal* were examined.
The data has been converted. The NA values have been removed using the *na.omit* function from the *data.table* package.
```{r}
library(data.table)
Team_Medal <- olimpic_cor %>% select(Team, Medal)
Team_Medal <- na.omit(Team_Medal)
```

The distribution of the number of medals among all teams was investigated.
```{r}
Team_amount_of_medals <- Team_Medal %>% group_by(Team) %>% summarise(amount_of_medals = n())
ggplot(Team_amount_of_medals, aes(Team, amount_of_medals))+geom_point()

```

The graph shows that the distribution can be divided into two parts according to the number of medals.The following graph shows the division of the distribution of the number of medals by medal type.An additional elevation has been added to the Y-axis.

```{r, echo=FALSE}
Team_amount_of_diff_medals <- Team_Medal %>% group_by(Team, Medal) %>% summarise(amount_of_diff_medals = n())
ggplot(Team_amount_of_diff_medals, aes(Team, amount_of_diff_medals, color = Medal))+
  geom_point()+
  scale_y_continuous(name = "Amount of diff medals", breaks = c(50, 100, 500, 1000, 1500, 2000, 2500))+
  facet_grid(.~ Medal)
```
The graph demonstrates a similar division across all three groups.It was determined that the data is divided into *two parts*: *teams with more than 50 medals* and *teams with less than 50 medals*.The data was divided into 2 groups.
```{r}
High_medal <- Team_amount_of_diff_medals %>% filter(amount_of_diff_medals > 50)
Low_medal <- Team_amount_of_diff_medals %>% filter(amount_of_diff_medals < 50)

```
#### Distribution of medals among teams with more than 50 medals
```{r, echo=FALSE}
ggplot(High_medal, aes(Team, amount_of_diff_medals, color = Medal))+
  geom_point()+
  facet_grid(.~ Medal)
```
#### Distribution of medals among teams with less than 50 medals
```{r, echo=FALSE}
ggplot(Low_medal, aes(Team, amount_of_diff_medals, color = Medal))+
  geom_point()+
  facet_grid(.~ Medal)
```

#### CONCLUSIONS:
1) Teams can be divided according to their level of training into teams with a high level and teams with a low level, as evidenced by the number of medals earned;

2) One could look at the composition of countries in these two groups, compare their GDP and spending on sports and try to relate living standards and incomes in the country with the success at the Olympics;

3) The type of medal, in this case, depends more on some other circumstances, since distribution in all groups is more or less the same.

Clustering techniques could be used to study the relationship between these variables. Nevertheless, based on their interaction, it can be assumed that there is a third variable (or a group of variables) that affects how many medals a team can receive (these influences will not apply to the type of medal).

### Conclusion
This paper demonstrates R's ability to explore a variety of data. A relatively large amount of data was processed using special tools of the R language. Several regularities were revealed between the anthropometric indicators of Olympic athletes. Also, the limitations in the use of standard methods of statistical testing of hypotheses with data of a sufficiently large volume were shown and the advantages of a graphical approach were shown.


```


